Across the full corpus of \num{3317} courses, feature adoption varies
widely both between and within the four taxonomy categories.
Table~\ref{tab:adoption_overview} lists all tracked features sorted by
adoption rate within each category, revealing a clear gradient from
broadly adopted to virtually unused features.

\subsection{Aggregate Adoption Rates}

\begin{table}[ht]
  \centering
  \caption{Adoption rates across all \num{3317} courses, sorted by rate
           within each category.  Features above \SI{10}{\percent} are
           set in the left column, those below in the right.}
  \label{tab:adoption_overview}
  \begin{tabular}{@{}llr@{\qquad}lr@{}}
    \toprule
    & \multicolumn{2}{c}{\textbf{Widely adopted}} &
      \multicolumn{2}{c}{\textbf{Rarely adopted}} \\
    \textbf{Category} & \textbf{Feature} & \textbf{\%} &
      \textbf{Feature} & \textbf{\%} \\
    \midrule
    \multirow{4}{*}{\textcolor{catPresentation}{Presentation}}
      & Narrator        & 58.6 & Galleries      &  7.3 \\
      & Animations      & 22.8 & Animated CSS   &  0.7 \\
      & TTS fragments   & 11.6 & TTS blocks     &  0.1 \\
      & Anim.\ blocks   & 11.0 & Effects        &  0.0 \\
    \midrule
    \multirow{6}{*}{\textcolor{catInteraction}{Interaction}}
      & Any quiz        & 45.5 & Single choice  &  9.0 \\
      & Text quiz       & 28.8 & Selection quiz &  7.3 \\
      & Multiple choice & 10.2 & Quiz hints     &  4.9 \\
      &                 &      & Task lists     &  4.7 \\
      &                 &      & Surveys        &  2.7 \\
      &                 &      & Matrix quiz    &  1.6 \\
    \midrule
    \multirow{3}{*}{\textcolor{catReuse}{Reuse}}
      & Macros (any)    & 72.1 & Custom macros  &  8.7 \\
      & Imports         & 59.6 &                &      \\
      & Ext.\ scripts   & 51.1 &                &      \\
    \midrule
    \multirow{4}{*}{\textcolor{catEmbedding}{Embedding}}
      & Math            & 48.0 & ASCII diagrams &  9.8 \\
      & Script tags     & 20.8 & WebApps        &  5.6 \\
      & HTML embeds     & 15.7 & Exec.\ code    &  3.1 \\
      &                 &      & Code projects  &  0.4 \\
    \bottomrule
  \end{tabular}
\end{table}

A first observation concerns the overall breadth of adoption:
of the \num{44} tracked features, only five fall below
\SI{1}{\percent} (effects, TTS blocks, classroom, code projects,
animated CSS).
The remaining 39~features --- \SI{89}{\percent} of the designed feature
space --- are used in measurable numbers.
LiaScript's feature palette is thus not ignored; it is \emph{explored},
albeit unevenly.

Within this broad adoption, the table reveals several category-specific
patterns.
\textcolor{catPresentation}{Presentation} features split sharply: narrator
and animations require minimal authoring effort (a single comment line
activates TTS) and achieve broad uptake, while fine-grained variants
remain near zero.
\textcolor{catReuse}{Reuse} features are driven by the import and macro system
--- most authors \emph{consume} shared libraries and macros but few
\emph{define} custom macros (\SI{8.7}{\percent}).
\textcolor{catInteraction}{Interaction} is dominated by quizzes
(\SI{45.5}{\percent}), but survey and matrix quiz types remain rare.
\textcolor{catEmbedding}{Embedding} features show the widest internal
spread: math notation reaches \SI{48.0}{\percent} in STEM-oriented
courses, while executable code (\SI{3.1}{\percent}) and code projects
(\SI{0.4}{\percent}) remain niche despite being a signature LiaScript
capability.

\subsection{Group-level Adoption Profiles}
\label{sec:profiles}

Table~\ref{tab:group_diff} lists features with notable adoption
differences across the four groups (spread $> 10$ percentage points).
The four-group segmentation --- splitting the former Community group
into Comm-Uni (\num{1178}~courses) and Comm-School (\num{186}~courses)
--- reveals patterns that were previously hidden in the aggregate.

\begin{table}[ht]
  \centering
  \caption{Features with divergent adoption rates across groups
           (spread $> 10$ pp, selection of most informative features).
           The highest value per row is set in \textbf{bold}.}
  \label{tab:group_diff}
  \begin{tabular}{llrrrr}
    \toprule
    \textbf{Category} & \textbf{Feature} &
      \textbf{Internal} & \textbf{\mintcol} & \textbf{Comm-Uni} & \textbf{Comm-Sch.} \\
    \midrule
    \multirow{5}{*}{\textcolor{catPresentation}{Presentation}}
      & Narrator       &  86.6 &   9.4 & \textbf{88.5} &  60.8 \\
      & TTS fragments  & \textbf{36.1} &   0.1 &  13.3 &   7.0 \\
      & Animations     & \textbf{66.2} &   0.6 &  29.7 &  29.6 \\
      & Logo           &  41.1 &   0.3 &  21.4 & \textbf{57.0} \\
      & Icon           &   9.7 &   0.0 &  24.1 & \textbf{46.2} \\
    \midrule
    \multirow{4}{*}{\textcolor{catInteraction}{Interaction}}
      & Any quiz       &  22.7 & \textbf{78.3} &  28.3 &  43.0 \\
      & Text quiz      &   9.7 & \textbf{70.0} &   4.9 &  15.6 \\
      & Selection quiz &   5.2 &   9.9 &   2.7 & \textbf{19.4} \\
      & Multiple choice&  11.3 &   0.8 &  17.2 & \textbf{18.3} \\
    \midrule
    \multirow{3}{*}{\textcolor{catReuse}{Reuse}}
      & Macros (any)   &  69.0 & \textbf{99.7} &  52.6 &  58.6 \\
      & Imports        &  57.4 & \textbf{98.3} &  31.7 &  45.7 \\
      & Ext.\ scripts  &  16.2 & \textbf{96.3} &  31.8 &  25.8 \\
    \midrule
    \multirow{6}{*}{\textcolor{catEmbedding}{Embedding}}
      & Code blocks    & \textbf{82.5} &   9.3 &  53.7 &  28.5 \\
      & Math           &  30.7 & \textbf{95.2} &  21.4 &  32.8 \\
      & ASCII diagrams & \textbf{38.5} &   2.3 &   8.3 &   5.4 \\
      & HTML embeds    &  20.4 &   5.9 &  20.5 & \textbf{39.2} \\
      & WebApps        &  13.0 &   0.7 &   4.8 & \textbf{24.2} \\
      & Audio          & \textbf{35.7} &   0.4 &  15.4 &  32.3 \\
    \bottomrule
  \end{tabular}
\end{table}

Four distinct profiles emerge from these divergences:

\paragraph{\mintgroup: template-driven workflow.}
\mintgroup{} dominates the Reuse category (macros~\SI{99.7}{\percent},
imports~\SI{98.3}{\percent}, external scripts~\SI{96.3}{\percent})
and relies heavily on text quizzes (\SI{70.0}{\percent}) and
math notation (\SI{95.2}{\percent}).
This profile reflects a standardised configuration for small,
self-contained STEM exercises: each course file imports a common set
of libraries (TikZ visualisation, Algebrite CAS) and uses text quizzes
as the primary interactive element.
Presentation features like narrator (\SI{9.4}{\percent}) and
animations (\SI{0.6}{\percent}) are nearly absent --- the exercise
format does not call for them.

\paragraph{Internal: feature showcase.}
The Internal group leads in code-oriented and presentation features
(code blocks~\SI{82.5}{\percent}, animations~\SI{66.2}{\percent},
ASCII diagrams~\SI{38.5}{\percent}, TTS fragments~\SI{36.1}{\percent}).
This is consistent with the developers' role as feature demonstrators and
early adopters of the full language surface.

\paragraph{Comm-Uni: narrative-textual style.}
Higher-education courses show the highest narrator adoption
(\SI{88.5}{\percent}), strong use of code blocks (\SI{53.7}{\percent}),
tables (\SI{45.8}{\percent}), and external CSS (\SI{43.0}{\percent}).
This profile suggests a lecture-oriented authoring style:
text-heavy, narrated content with structured data presentation
but comparatively little multimedia embedding or interactive elements.

\paragraph{Comm-School: multimedia-interactive style.}
School-level courses present a strikingly different profile.
They lead in visual branding (logo~\SI{57.0}{\percent},
icon~\SI{46.2}{\percent}), multimedia embedding
(audio~\SI{32.3}{\percent}, video~\SI{26.9}{\percent},
HTML embeds~\SI{39.2}{\percent}, WebApps~\SI{24.2}{\percent}),
and favour selection-based quiz types
(selection quiz~\SI{19.4}{\percent}, multiple choice~\SI{18.3}{\percent}).
This reflects a pedagogy oriented toward engagement through
varied media and familiar interactive formats rather than code or
narrated text.

\mintgroup{} and Comm-School both target school-level education but
arrive at high feature adoption through opposite routes: a centralised
template system versus per-course authoring decisions.
Educational context alone therefore does not determine the feature
profile --- the \emph{authoring infrastructure} is equally decisive.
