% ~750 words
% Five subsections: target audience, gap analysis, adoption ladder, survey, monitoring

The adoption data raises a fundamental strategic question:
should development effort target the many occasional authors who
plateau at narrator and quizzes, or the few prolific authors who
might exploit the full feature space?
The corpus provides a clear empirical answer.
Of the 197~Community accounts, 82 have produced exactly one course and
81 have produced two to ten.
Yet the eight most prolific accounts (56--146~courses each) exhibit
essentially the same feature profile as occasional contributors
(Section~\ref{sec:three_groups}).
Production volume does not drive feature exploration.
This means that investing exclusively in power-user features
(e.g.\ code projects, adaptive learning paths) addresses a small
audience without broadening the overall feature uptake.
Conversely, the MINT-the-GAP model demonstrates that
\emph{infrastructure-level} choices --- a standardised configuration
that pre-selects shared libraries and exercise formats --- can lift
adoption of specific features for an entire author community at once.
The implication is that the most effective improvements operate
at the boundary between casual and intermediate use, lowering the
step from the current adoption plateau to the next rung of the
feature ladder.

The adoption gradient itself can be explained through three gap classes.

\subsection{Three Adoption Gap Classes}
\label{sec:gap_classes}

\paragraph{Documentation deficit.}
Some features are syntactically non-obvious and lack progressive
examples.
Consider the contrast between narrator and effects:
activating text-to-speech requires a single header line
(\texttt{<!--~narrator:~German~Female~-->}), whereas timed content
appearance demands a numeric fragment notation
(\texttt{\{\{1\}\}}, \texttt{\{\{2-3\}\}}) combined with block
delimiters (\texttt{--\{\{1\}\}--}) for accompanying audio ---
a secondary syntax layer documented primarily through a single,
comprehensive reference rather than graduated tutorials.
The strong adoption of narrator (\SI{84}{\percent} in the Community)
and basic macros (\SI{54}{\percent}) shows that authors \emph{do}
progress beyond plain Markdown when the entry cost is low.
The three-group comparison reinforces this interpretation: Community
authors show significantly lower adoption of animation and script
features than Internal authors, although the underlying syntax is
identical --- suggesting that existing documentation does not
sufficiently bridge the gap.
A survey participant independently confirmed this barrier:
\emph{``Kompaktere, auszugsweise Dokumentation für Einsteiger''}
(priority~4/5), while another requested
\emph{``Einführung verschiedener Rollen [im Editor], die
unterschiedliche Anzahl von Feature-Buttons gezeigt bekommen
(Novice, Power User)''} (priority~4/5).

\paragraph{Workflow barrier.}
Code projects and executable code require authors to configure external
services (CodeRunner templates via \texttt{import:}) and understand the
interaction between named code blocks (\texttt{+}/\texttt{-} visibility
prefixes, filename annotations).
For educators without a technical background this represents a barrier
that documentation alone cannot resolve.
The survey confirms this concretely:
\emph{``Bildausgaben beim Coderunner sind umständlich, das
Terminalfenster muss erst vergrößert werden''} (priority~3/5),
and \emph{``Devserver produziert anderen Code als die Live Version''}
(priority~5/5), indicating that even experienced authors encounter
friction in the embedding workflow.
Priorities include a visual \emph{template picker} that inserts
pre-configured embedding blocks, improved error messages when external
templates fail, and a default code execution sandbox requiring no
configuration.

\paragraph{Configuration lock-in.}
The MINT-the-GAP profile demonstrates that a standardised configuration
--- importing the same libraries (TikZ, Algebrite) across all exercise
files --- can drive near-universal adoption of specific features
(math~\SI{95}{\percent}, imports~\SI{98}{\percent}), but simultaneously
leaves features outside this scope unexplored
(narrator~\SI{9}{\percent}, animations~\SI{0.6}{\percent}).
This pattern represents a design tension: standardised configurations
lower the entry barrier for a predefined feature set but discourage
exploration beyond it.
The survey reveals related friction:
\emph{``Kompatibilität zu Standard-MD herstellen~[\ldots] Es gibt
eine größere Liste von Situationen wo sich LiaScript-MD nicht wie
echtes MD verhält''} (priority~4/5) points to frustration when
LiaScript-specific syntax diverges from author expectations.
Future shared configurations should expose optional extension points
so that standardised workflows do not inadvertently narrow the
feature space.

\paragraph{Convergent adoption floors.}
Several features remain below \SI{5}{\percent} in \emph{all} three
groups, including among the core developers themselves
(animated CSS~\SI{2.4}{\percent}, code
projects~\SI{1.3}{\percent}, effects~\SI{0}{\percent}).
Unlike the documentation deficit, where Internal adoption proves that
the feature \emph{can} succeed, these convergent floors suggest that the
features' current design may not match real authoring needs.
They warrant a critical review of whether the feature concepts
themselves require rethinking rather than better documentation.

\subsection{The Adoption Ladder}
\label{sec:ladder}

Community adoption rates suggest a natural progression path:
narrator and links ($>$\,\SI{80}{\percent}) $\to$
macros and tables ($\approx$\,\SI{50}{\percent}) $\to$
quizzes and animations ($\approx$\,\SI{25}{\percent}) $\to$
embedding features ($<$\,\SI{10}{\percent}).
The power-user analysis in Section~\ref{sec:three_groups} shows that
prolific Community authors (\num{8}~accounts with 56--146~courses each)
exhibit essentially the same feature profile as occasional contributors,
indicating that production volume alone does not drive feature
exploration.
Onboarding documentation should therefore follow this ladder explicitly,
guiding authors from high-adoption to low-adoption features in a
structured sequence rather than presenting all capabilities as
equally accessible.

\subsection{Qualitative Triangulation}
\label{sec:triangulation}

Beyond the individual quotes cited above, the survey reveals a
cross-cutting theme: four of the 60~items request
\emph{AI-assisted course generation}, making it the most prominent
cluster.
One participant described an
\emph{``Agentensystem zur Kurserstellung mit Human-in-the-middle
[\ldots] Die AI stellt Rückfragen und erstellt dann einen Kurs,
dieser wird von einem AI-Linter gegengecheckt''} (priority~2/5).
Combined with the configuration lock-in finding, this suggests that
AI-based generation could fulfil the same adoption-enabling role as
standardised configurations --- lowering the entry cost for complex
features --- while avoiding the narrowing effect of fixed setups.
Two further items request a \emph{syntax checker or linter}
(\emph{``LiaScript Linter''}, priority~2/5;
\emph{``Bessere Fehlermeldungen bei Syntaxfehlern''}, priority~3/5),
reinforcing that real-time authoring feedback is perceived as
insufficient across experience levels.

\subsection{Monitoring Future Adoption}

Because LiaScript's architecture precludes runtime telemetry,
repeating the GitHub corpus analysis at regular intervals
is the only mechanism available for tracking whether these improvements
translate into changed authoring behaviour.
We recommend treating the corpus snapshot as an annual instrument,
analogous to a developer survey in the open-source context.
