% ~250 words

This paper presented the first systematic empirical analysis of feature
adoption in the LiaScript ecosystem, which follows a sovereignty-by-design approach.
Exploiting the GitHub corpus as the only observable proxy for a
tool with no server-side telemetry, we analysed \num{3317} validated
courses contributed by \num{314} committers using a four-category
feature taxonomy; the \num{2973} courses with a clear education-level
classification enter the four-group segmentation.
The central finding is that \SI{89}{\percent} of the designed feature
space is adopted in measurable numbers: only five of 44~tracked
features fall below \SI{1}{\percent} course-level containment.
LiaScript's designed palette is thus broadly reached; the challenge
is not that features go unused, but that each author community
explores only its own subset.
The four-group comparison reveals structurally different adoption
ladders for university and school educators, and shows that authoring
infrastructure shapes adoption as strongly as pedagogical
needs.
These findings translate into three concrete priorities
(Section~\ref{sec:implications}):
role-specific onboarding that mirrors the distinct adoption ladders
of university and school authors,
reduced embedding complexity to lower the entry barrier for
non-technical educators,
and open shared configurations that lift adoption without narrowing
the explored feature space.

Beyond static documentation, the context-specific adoption profiles
identified in this study open a promising avenue for AI-assisted
authoring.
\ifanonymous
{\color{orange}An AI-based authoring assistant for LiaScript
[self-citation suppressed for blind review] guides educators through
the process of creating interactive courses.}
\else
The LiaScript Teaching Agent~\cite{TeachingAgent2025} is an AI-based
assistant that guides educators through the process of creating
interactive courses.
\fi
Currently, such agents treat the full feature space uniformly ---
they can explain any feature but lack empirical grounding for
\emph{which} features to recommend to \emph{whom}.
The adoption ladders and gap classes derived in this work provide
exactly this grounding: they allow the agent to tailor its
suggestions to the author's context.
Rather than presenting the full feature catalogue, the agent would
operate as a \emph{personalised onboarding companion} that meets
authors where they are and nudges them toward the features most
likely to enrich their specific course type.
This closes the loop between corpus analysis and authoring practice:
empirical adoption data informs the agent's recommendations, and
repeated corpus analyses can evaluate whether agent-assisted
authoring shifts the adoption profiles over time.

Because LiaScript's architecture precludes runtime telemetry,
repeating the GitHub corpus analysis at regular intervals is the only
mechanism for tracking whether these improvements translate into changed
authoring behaviour.
Beyond feature adoption, the underlying dataset opens substantial
further research opportunities:
the full commit history enables longitudinal studies of how courses
evolve and how long they remain actively maintained;
fork and multi-author patterns reveal collaboration structures
across institutions;
and cross-referencing feature trajectories with repository activity
can identify which onboarding paths lead to sustained authoring
engagement.
A companion study will explore these dimensions --- course lifecycle,
collaboration dynamics, and the validity of GitHub engagement metrics
as indicators of educational impact in a system that, by design,
leaves no usage trace.
